### 2015-05-12 evaluation.tex
some fixes

We performed experiments to validate the usefulness of the \whoop approach (Section~\ref{whoop}) and its combination with \corral (Section~\ref{corral}). We first present race-checking results from running \whoop and \corral on \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel distribution.\footnote{\url{https://www.kernel.org}} We then evaluate the runtime performance and scalability of \corral and \whoop + \corral with different yield instrumentation granularities and context-switch bounds.
Our results demonstrate that \whoop can efficiently accelerate bug-finding with \corral.

@@

\noindent
\textbf{Race-Checking}\xspace\xspace Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of potentially racy pairs identified by \whoop (\#Racy Pairs); number of potentially racy memory regions reported by \whoop (\#Racy MRs); and number of races that discovered by \corral using a context-switch bound of 2 (\#Races Found). We did not discover new races with larger context-switch bounds. This might mean that these drivers only have races that manifest with at least one or two context-switches, or that \corral hit its bounds before discovering a deeper race.

@@

As an example of the second case, we found the following race in the generic\_nvram char driver (see Example~\ref{fig:data_race_example} for the source code): during the \texttt{llseek} entry point, the driver is accessing the file offset \texttt{file->f\_pos} without first acquiring a lock (\texttt{file} is passed as a parameter to \texttt{llseek}). This can lead to a race if the driver invokes \texttt{llseek} from another thread passing the same \texttt{file} object as a parameter. When we investigated another char driver that uses the same APIs, we saw that it was protecting the offset access in its \texttt{llseek} entry point with a mutex. This made us suspicious that the race we found in generic\_nvram could be real. We filed a bug report, but did not manage to get a response yet.

>>>>

We performed experiments to validate the usefulness of the \whoop approach (Section~\ref{whoop}) and its combination with \corral (Section~\ref{corral}). We first present race-checking results from running \whoop and \corral on \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel distribution.\footnote{\url{https://www.kernel.org}} We then evaluate the runtime performance and scalability of \corral and \whoop + \corral with different yield instrumentation granularities and context-switch bounds.
Our results demonstrate that \whoop can efficiently accelerate race-checking with \corral.

@@

\noindent
\textbf{Race-Checking}\xspace\xspace Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of potentially racy pairs identified by \whoop (\#Racy Pairs); number of potentially racy memory regions reported by \whoop (\#Racy MRs); and number of races discovered by \corral using a context-switch bound of 2 (\#Races Found). We did not discover new races with larger context-switch bounds. This might mean that these drivers only have races that manifest with at least one or two context-switches, or that \corral hit its bounds before discovering a deeper race.

@@

As an example of the second case, we found the following race in the generic\_nvram char driver (see Figure~\ref{fig:data_race_example} for the source code): during the \texttt{llseek} entry point, the driver is accessing the file offset \texttt{file->f\_pos} without first acquiring a lock (\texttt{file} is passed as a parameter to \texttt{llseek}). This can lead to a race if the driver invokes \texttt{llseek} from another thread passing the same \texttt{file} object as a parameter. When we investigated another char driver that uses the same APIs, we saw that it was protecting the offset access in its \texttt{llseek} entry point with a mutex. This made us suspicious that the race we found in generic\_nvram could be real. We filed a bug report, but did not manage to get a response yet.
